A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
paper update - modified graph heights

---
title: "A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model"
subtitle: "The Impact of Pollster Differences, Population Type, and Poll Recency on Predicting Support for Kamala Harris"
author: 
  - Jiwon Choi
  - Kevin Roe
thanks: "Code and data are available at: [https://github.com/jwonc4602/2024_US_Election_Forecast](https://github.com/jwonc4602/2024_US_Election_Forecast)."
date: today
date-format: long
abstract: "The 2024 U.S. Presidential Election has far-reaching global implications for economic, environmental, and social policy, making it a focal point for international attention. This paper applies a Bayesian generalized linear model to analyze trends in Kamala Harris' support, accounting for pollster differences, population types, and poll recency. Despite steady support at 48%, Harris is projected to lose the national popular vote and key battleground states to Donald Trump. Our findings emphasize the significance of polling methodologies and their role in predicting U.S. policy outcomes. Future research should incorporate the Electoral College to address current limitations."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

# Plot distribution using histogram
ggplot(prediction, aes(x = predicted_pct)) + 
  geom_histogram(binwidth = 3, fill = "green", alpha = 0.7, color = "black") +
  theme_minimal() + 
  labs(x = "Predicted Percentage of Support (predicted_pct)", 
       y = "Count")
```
\newpage

@@

```
\newpage
```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-populationtype
#| fig-cap: Distribution of population type
#| fig-width: 5
#| fig-height: 5
#| fig-align: center

# Plot distribution of Population Type using histogram
ggplot(prediction, aes(x = population)) +
  geom_bar(fill = "orange", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Population",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
\newpage

@@

```
\newpage
```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-recency
#| fig-cap: Distribution of on the amount of polls collected in 30 days 
#| fig-width: 5 
#| fig-height: 5
#| fig-align: center

@@

Please find the proposed question list for the online survey attached [here](https://forms.gle/AFqodUEk48o864aN6).

>>>>

---
title: "A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model"
subtitle: "The Impact of Pollster Differences, Population Type, and Poll Recency on Predicting Support for Kamala Harris"
author: 
  - Jiwon Choi
  - Kevin Roe
thanks: "Code and data are available at: [https://github.com/jwonc4602/2024_US_Election_Forecast](https://github.com/jwonc4602/2024_US_Election_Forecast)."
date: today
date-format: long
abstract: "The 2024 U.S. Presidential Election has far-reaching global implications for economic, environmental, and social policy, making it a focal point for international attention. This paper applies a Bayesian generalized linear model to analyze trends in Kamala Harris' support, accounting for pollster differences, population types, and poll recency. Despite steady support at 48%, Harris is projected to lose the national popular vote and key battleground states to Donald Trump. Our findings highlight the impact of polling methodologies and their role in shaping predictions of U.S. policy outcomes. Future research should incorporate the Electoral College to address current limitations."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

# Plot distribution using histogram
ggplot(prediction, aes(x = predicted_pct)) + 
  geom_histogram(binwidth = 3, fill = "green", alpha = 0.7, color = "black") +
  theme_minimal() + 
  labs(x = "Predicted Percentage of Support (predicted_pct)", 
       y = "Count")
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-populationtype
#| fig-cap: Distribution of population type
#| fig-width: 5
#| fig-height: 2.5
#| fig-align: center

# Plot distribution of Population Type using histogram
ggplot(prediction, aes(x = population)) +
  geom_bar(fill = "orange", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Population",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-recency
#| fig-cap: Distribution of on the amount of polls collected in 30 days 
#| fig-width: 5 
#| fig-height: 2.5
#| fig-align: center

@@

Please find the proposed question list for the online survey attached [here](https://forms.gle/AFqodUEk48o864aN6).
\newpage
